Physcraper: A Python package for continually updated gene trees

### 2020-05-13 phylota-overview.Rmd
some more phylota examples

1. As an example of a tool that mines GenBank data for phylogenetic reconstruction:
  - original publication of PHLAWD [@smith2009mega]
  - an analysis identifying research priorities and data requirements for resolving
  the red algal tree of life [@verbruggen2010data]
  - a review for ecologists about phylogenetic tools [@roquet2013building]

1. When the software was actually used to construct (partially or in full) a DNA
data set to be used for phylogenetic reconstruction:
  - A 1000 tip phylogeny of the family of the nightshades [@sarkinen2013solanaceae]
  - A 56 tip phylogeny of crustacean zooplancton [@helmus2010communities] -- ecological study
  - A 63 tip phylogeny of the Salmonidae family [@crete2012salmonidae]
  - A 321 tip phylogeny of Testudines [@thomson2010sparse]
  - A 69 taxa phylogeny of the family Cyprinodontidae of the pupfish [@martin2011trophic]
  - A 2,957 taxa phylogeny of the class Moniloformopses of living ferns [@lehtonen2011towards]
  - A 2,573 species phylogeny of the Papilionoidea [@hardy2014specialization]
  - A 23 taxa phylogeny of the California flora [@anacker2011origins]
  - Phylogenies of 6 different clades of flowering plants representing an independent
  evolutionary origin of extrafloral nectaries: *Byttneria* (Malvaceae), *Pleopeltis* (Polypodiaceae),
  *Polygoneae* (Polygoneaceae), *Senna* (Fabaceae), *Turnera* (Passifloraceae), and *Viburnum*
  (Adoxaceae) [@weber2014defense].
  - To supplement DNA data sets of various pre-existing mammalian phylogenetic trees
  sampled at different taxonomic levels [@faurby2015species]
  -

>>>>

1. As an example of a tool that mines GenBank data for phylogenetic reconstruction:
  - original publication of PHLAWD [@smith2009mega]
  - an analysis identifying research priorities and data requirements for resolving
  the red algal tree of life [@verbruggen2010data]
  - a review for ecologists about phylogenetic tools [@roquet2013building]
  - a study constructing a dated seed plant phylogeny using pyPHLAWD [@smith2018constructing]
  - a study presenting an assembly and alignment free method for phylogenetic reconstruction
    using genomic data, that aims to be incorporated in a tool as phylota some day [@fan2015assembly]
  - nexml format presentation [@vos2012nexml] - cites phylota as a tool that uses
    stored phyloinformatic data that could benefit from adopting nexml, to increase
    interoperability
  - a study of fruit evolution, analysing a previously published phylogeny of 8911
    tips of the Campanulidae, constructed with PHLAWD [@beaulieu2013fruit]
  - a study of Southeast Asia plant biodiversity inventory [@webb2010biodiversity] -
    cites phylota as a tool that would allow rapid phylogentic placing of newly
    discovered species, and generation of phylogenetically informed guides for field
    identification.

1. When the software was actually used to construct (partially or in full) a DNA
data set to be used for phylogenetic reconstruction:
  - A 1000 tip phylogeny of the family of the nightshades [@sarkinen2013solanaceae]
  - A 56 tip phylogeny of crustacean zooplancton [@helmus2010communities] -- ecological study
  - A 63 tip phylogeny of the Salmonidae family [@crete2012salmonidae]
  - A 321 tip phylogeny of Testudines [@thomson2010sparse]
  - A 69 taxa phylogeny of the family Cyprinodontidae of the pupfish [@martin2011trophic]
  - A 2,957 taxa phylogeny of the class Moniloformopses of living ferns [@lehtonen2011towards]
  - A 2,573 species phylogeny of the Papilionoidea [@hardy2014specialization]
  - A 23 taxa phylogeny of the California flora [@anacker2011origins]
  - Phylogenies of 6 different clades of flowering plants representing an independent
  evolutionary origin of extrafloral nectaries: *Byttneria* (Malvaceae), *Pleopeltis* (Polypodiaceae),
  *Polygoneae* (Polygoneaceae), *Senna* (Fabaceae), *Turnera* (Passifloraceae), and *Viburnum*
  (Adoxaceae) [@weber2014defense].
  - To supplement DNA data sets of various pre-existing mammalian phylogenetic trees
  sampled at different taxonomic levels [@faurby2015species]
  - A 900 species tree of muroid rodents, Muroidea [@steppan2017muroid], where 300
    species were newly added by the study and the rest obtained using phylota.
  - A 95 taxa phylogeny of Gymnosperms, focused on Ephedra, Gnetales [@ickert2009fossil]
  - A 1061 genera phylogeny of the Oscine birds [@selvatti2015paleogene]
  - A 268 species phylogeny of sharks, representing all orders and 32 families [@sorenson2014effect]

### 2020-05-13 physcraper_ms.Rmd
some more phylota examples

---
title: 'Physcraper: A Python package for continually updated gene trees'
date: 'Manuscript rendered on `r format(Sys.time(), "%d %B, %Y")`'
author:
  - Luna L. Sanchez Reyes, University of California, Merced
  - Martha Kandziora, University of California, Merced
  - Emily Jane McTavish, University of California, Merced
output:
  redoc::redoc
bibliography: paper.bib
csl: apa.csl
---

@@

# Tools on a similar track:

Tools that do similar things:
pyPhlawd [@smith2019pyphlawd]
SUPERSMART [@antonelli2017toward]

>>>>

---
title: 'Physcraper: A Python package for continually updated gene trees'
author:
  - Luna L. Sanchez Reyes
  - Martha Kandziora
  - Emily Jane McTavish
  - University of California, Merced
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: paper.bib
csl: apa.csl
output:
  redoc::redoc
---

@@

# Tools on a similar track

Tools that do similar things at different levels:

Phylota [@sanderson2008phylota] - cited by 122 studies.

PHLAWD [@smith2009mega] and pyPhlawd [@smith2019pyphlawd] - baited analyses

A [ruby pipeline](https://www.zfmk.de/en/research/research-centres-and-groups/taming-of-an-impossible-child-pipeline-tools-and-manuals),
only available from the [supplementary data](https://static-content.springer.com/esm/art%3A10.1186%2F1741-7007-9-55/MediaObjects/12915_2011_480_MOESM1_ESM.ZIP)
of the journal [[@peters2011taming]](https://bmcbiol.biomedcentral.com/articles/10.1186/1741-7007-9-55#Sec21)

PUmPER [@izquierdo2014pumper] - perpetual updating with newly added sequences to
GenBank

SUMAC [@freyman2015sumac] -  both “baited” analyses and single‐linkage clustering
methods, as well as a novel means of determining when there are enough overlapping data in the DNA matrix

SUPERSMART [@antonelli2017toward] - baited analyses up to bayesian divergente time
estimation

SOPHI - [@chesters2017construction] - Searches DNA sequence data from repos other
than GenBank, such as transcriptomic and barcoding repos.

PhySpeTre [@fang2019physpetree] - no sequence retrieval, just phylogenetic reconstruction
pipeline.
